DATA 624 Homework 6

### 2020-03-17 DATA624/HW6.Rmd
More work on HW 6

```{r}
ggtsplot(diff(usnetelec, 1), "Differenced US Net Electricity Generation (lag=1)")
```

```{r}
#ur.kpss(diff(usnetelec, 1)) 
#Box.test(diff(usnetelec, 1), lag = 1)
usnetelec %>% diff() %>% ur.kpss() %>% summary()
```

@@

```{r}
ggtsdisplay(diff(usgdp), "US GDP")
```

@@

@@

@@

>>>>

```{r}
autoplot(usnetelec, main = "US Net Electricity Generation") +
  theme(axis.title = element_blank())
```

**The trend looks nearly linear.  It will probably only need to be differenced to be stationary.  I will use the `ndiffs` function to determine the order of differencing.***

```{r}
ggtsplot(diff(usnetelec, ndiffs(usnetelec)), paste0("Differenced US Net Electricity Generation (lag=", ndiffs(usnetelec), ")"))
```

**It needed to be differenced by `r ndiffs(usnetelec)`.  This is further confirmed using the KPSS Unit Root test below:**

```{r}
usnetelec %>% diff() %>% ur.kpss() %>% summary()
```

@@

```{r}
autoplot(usgdp, main = "Quarterly US Gross Domestic Product") +
  theme(axis.title = element_blank())
```

**Since this series is dollars we probably need to log transform it.  It also looks like it needs to be differenced.**

```{r}
usgdp_lambda <- BoxCox.lambda(usgdp)
bc_usgdp <- BoxCox(usgdp, lambda = usgdp_lambda)
ggtsplot(diff(bc_usgdp, ndiffs(bc_usgdp)), paste0("Differenced Quarterly US GDP (lag=", ndiffs(bc_usgdp), ", lambda=",round(usgdp_lambda,2),")"))
```

```{r}
bc_usgdp %>% diff() %>% ur.kpss() %>% summary()
```

@@

```{r}
autoplot(mcopper, main = "Monthly Grade A Copper Prices") +
  theme(axis.title = element_blank())
```

```{r}
mcopper_lambda <- BoxCox.lambda(mcopper)
bc_mcopper <- BoxCox(mcopper, lambda = mcopper_lambda)
ggtsplot(diff(bc_mcopper, ndiffs(bc_mcopper)), paste0("Differenced Monthly Grade A Copper Prices (lag=", ndiffs(bc_mcopper), ", lambda=",round(mcopper_lambda,2),")"))
```

@@

```{r}
autoplot(enplanements, main = "Monthly US Domestic Enplanements") +
  theme(axis.title = element_blank())
```

```{r}
enplanements_lambda <- BoxCox.lambda(enplanements)
bc_enplanements <- BoxCox(enplanements, lambda = enplanements_lambda)
ggtsplot(diff(bc_enplanements, ndiffs(bc_enplanements)), paste0("Differenced Monthly US Domestic Enplanements (lag=", ndiffs(bc_enplanements), ", lambda=",round(enplanements_lambda,2),")"))
```

@@

```{r}
autoplot(visitors, main = "Monthly Australian Overseas Visitors") +
  theme(axis.title = element_blank())
```

```{r}
visitors_lambda <- BoxCox.lambda(visitors)
bc_visitors <- BoxCox(visitors, lambda = visitors_lambda)
ggtsplot(diff(bc_visitors, ndiffs(bc_visitors)), paste0("Differenced Monthly Australian Overseas Visitors (lag=", ndiffs(bc_visitors), ", lambda=",round(visitors_lambda,2),")"))
```
